## Elastic Net Regression with simpleEnsembleGroup6

### Overview

Elastic net regression is a regularized regression method that linearly combines the penalties of the lasso and ridge methods. The technique encourages a sparse model like lasso, while maintaining the regularization properties of ridge regression. It's particularly useful when dealing with highly correlated data.

### Getting Started

#### Installing and Loading Required Packages

Ensure that both simpleEnsembleGroup6 and glmnet are installed and loaded, as glmnet is used for performing elastic net regression:

```{r}
# Install glmnet if it's not already installed
if (!require(glmnet)) install.packages("glmnet", dependencies = TRUE)

# Load necessary libraries
library(simpleEnsembleGroup6)
library(glmnet)
```

### Data Preparation

#### Example Dataset

For our example, we will use the mtcars dataset, which includes various automotive measurements. The goal is to predict mpg (miles per gallon) using other characteristics.

```{r}
# Load the mtcars dataset
data(mtcars)
head(mtcars)
```

#### Preprocessing Steps

Preparation of data includes selecting the variables and ensuring they are suitable for modeling:

```{r}
# Handle missing values if any
mtcars <- na.omit(mtcars)

# Select predictors and ensure they are in the correct format
X <- as.matrix(mtcars[, -which(names(mtcars) == "mpg")])  # Exclude 'mpg' from predictors
y <- mtcars$mpg  # Response variable
```

### Fitting an Elastic Net Model

The elastic_net_regression function is tailored to handle the nuances of fitting an elastic net model, including the choice of alpha and lambda.

#### Function Usage

Set alpha to balance between ridge (alpha=0) and lasso (alpha=1) regression. Here, we set alpha to 0.5 as a starting point:

```{r}
# Fitting the elastic net model
model <- elastic_net_regression(y, X, alpha = 0.5)
```

### Results and Interpretation

Evaluating the model involves looking at the coefficients and the overall model fit:

```{r}
# Print the model coefficients
print(coef(model))

# Plot the coefficients path
plot(model)
```

These outputs help in understanding how each predictor affects the response variable and how robust the model is to multicollinearity.

### Model Tuning

Lambda is a critical parameter in regularization. It controls the strength of the penalty applied to the model:

```{r}
# Optimal lambda selection through cross-validation
cv_model <- cv.glmnet(X, y, alpha = 0.5)
plot(cv_model)
best_lambda <- cv_model$lambda.min
cat("Best lambda:", best_lambda)

# Refit the model with the best lambda
best_model <- elastic_net_regression(y, X, alpha = 0.5, lambda = best_lambda)
```

### Conclusion

This vignette has introduced how to effectively apply elastic net regression using the elastic_net_regression function from the simpleEnsembleGroup6 package. With its ability to handle various data complexities, elastic net regression is a valuable addition to any data scientist's toolkit.

For more detailed exploration and further functionalities, refer to the glmnet package documentation:

```{r}
?glmnet
?elastic_net_regression
```
