## Ensemble Learning with simpleEnsembleGroup6

### Overview

Ensemble learning is a powerful technique that combines the strengths of multiple models to improve the overall predictions. It's particularly effective in reducing variance (bagging), bias (boosting), or improving predictions (stacking). The ensemble_learning function supports both averaging for regression and majority voting for classification, allowing it to be versatile across different types of modeling tasks.

### Getting Started

#### Loading the Package

Make sure that simpleEnsembleGroup6 is loaded:

```{r}
# Load necessary libraries
library(simpleEnsembleGroup6)
```

### Data Preparation

#### Example Dataset

Let's use the mtcars dataset as an example. We will predict the mpg (miles per gallon) using other car attributes.

```{r}
# Load the mtcars dataset
data(mtcars)
# Prepare predictors and response
X <- mtcars[, -which(names(mtcars) == "mpg")]
y <- mtcars$mpg
```

### Using the ensemble_learning Function

This function orchestrates the process of fitting multiple models and combining their predictions.

#### Function Parameters

-   *X*: Dataframe of predictors.
-   *y*: Vector of the response variable.
-   *model_functions*: A list of functions that model data. Each function should accept a response and predictors and return a fitted model.
-   *method*: Specifies how to combine the model predictions: "average" for regression and "vote" for classification.

#### Function Usage

Here’s how to use the function with a simple linear model and a generalized linear model for demonstration:

```{r}
# Define a simple linear model function
lm_model <- function(y, X) {
  lm(y ~ ., data = as.data.frame(cbind(X, y)))
}

# Define a simple GLM model function for demonstration
glm_model <- function(y, X) {
  glm(y ~ ., family = gaussian(), data = as.data.frame(cbind(X, y)))
}

# Running the ensemble learning function
results <- ensemble_learning(X, y, model_functions = list(lm_model, glm_model), method = "average")
```

### Results and Interpretation

After running the function, you'll get combined predictions based on the averaging of outputs from the linear and GLM models.

```{r}
# Print the combined predictions
print(results)
```

### Details of the Process

1.  *Data Splitting*: The data is divided into training and testing sets based on a specified test size.
2.  *Model Fitting*: Each model function is applied to the training data.
3.  *Prediction Aggregation*: Predictions from each model are combined. If the method is "average," the predictions are averaged. If "vote," the majority vote is calculated for each observation.
4.  *Response Handling*: Automatically detects if the response variable is for classification or regression and adapts the prediction method accordingly.

### Conclusion

The ensemble_learning function provides an efficient way to leverage the strengths of multiple modeling approaches, enhancing predictive accuracy and reliability. This method is highly recommended for complex datasets where a single model might not capture all the nuances of the data.

For further exploration of ensemble methods, consider experimenting with different combinations of models and aggregation techniques to find the best setup for your specific dataset.
