---
title: "Linear or Logistic Regression Tutorial"
author: 
  - "Group 6"
date: "2024-05-03"
output: 
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear or Logistic Regression Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Regression Analysis with simpleEnsembleGroup6

### Overview

Regression analysis is fundamental to predictive modeling, providing insights into relationships between dependent and independent variables. In simpleEnsembleGroup6, the function linear_logistic_regression() is designed to adaptively choose between linear and logistic regression based on the type of the response variable. This vignette details the use of this function using the mtcars dataset.

### Getting Started

#### Installing and Loading the Package

First, ensure that the simpleEnsembleGroup6 package is installed and loaded into your R environment:

```{r}
# Install the package if it's not already installed (uncomment the next line)
# install.packages("simpleEnsembleGroup6")

# Load the package
library(simpleEnsembleGroup6)
```

### Data Preparation

#### The mtcars Dataset

The mtcars dataset contains data from Motor Trend's 1974 car road tests. It includes various metrics such as miles per gallon, displacement, horsepower, and weight.

```{r}
# Load and examine the mtcars dataset
data(mtcars)
head(mtcars)
```

#### Preprocessing Steps

Proper data preparation is key to successful model fitting. Here, we'll standardize some predictors and check for missing values.

```{r}
# Check for and handle missing values
if (anyNA(mtcars)) {
  mtcars <- na.omit(mtcars)
}

# Standardize predictors to have mean zero and unit variance
mtcars$disp <- scale(mtcars$disp)
mtcars$hp <- scale(mtcars$hp)
mtcars$wt <- scale(mtcars$wt)

# Select the response variable and predictors
y <- mtcars$mpg
X <- mtcars[, c("disp", "hp", "wt")]
```

### Model Fitting

Using the prepared dataset, we apply the linear_logistic_regression function to fit an appropriate regression model.

#### Function Usage

```{r}
# Fitting the model
model <- linear_logistic_regression(y, X)
```

### Results and Interpretation

Once the model is fitted, the next step is to interpret the results to understand the effect of each predictor on the response variable.

```{r}
# Display the summary of the model
summary(model)
```

This vignette provided a complete guide on using the linear_logistic_regression function from the simpleEnsembleGroup6 package. It covered theoretical foundations, data preparation, model fitting, and result interpretation, equipping users with the necessary tools to perform regression analysis on their datasets.

For further information, refer to the function's help page within R:

```{r}
?linear_logistic_regression
```
