## Feature Selection by Correlation with simpleEnsembleGroup6

### Overview

Feature selection is a crucial step in model building, especially in datasets with many variables. The pre_screen_predictors_corr function simplifies this process by calculating the Pearson correlation coefficient between each predictor and the response variable, and then identifying the predictors with the highest absolute correlations.

### Getting Started

#### Loading the Package

Before using the pre_screen_predictors_corr function, make sure simpleEnsembleGroup6 is loaded:

```{r}
# Load the necessary library
library(simpleEnsembleGroup6)
```

### Data Preparation

#### Example Dataset

For demonstration, let's use the mtcars dataset. Assume we are interested in finding predictors that are most linearly related to mpg (miles per gallon).

```{r}
# Load the mtcars dataset
data(mtcars)
```

### Using the pre_screen_predictors_corr Function

This function streamlines the initial step in feature selection by focusing on correlation, a measure of linear association.

#### Function Usage

Here’s how to use the function to find the top predictors for mpg:

```{r}
# Running the feature selection function
y <- mtcars$mpg
X <- as.matrix(mtcars[, -which(names(mtcars) == "mpg")])
top_predictors <- pre_screen_predictors_corr(X, y, top_k = 5)
```

### Results and Interpretation

After running the function, it's useful to examine which predictors are most strongly correlated with the response variable:

```{r}
# Print the top predictors
print(top_predictors)
```

This will give you a list of the top 5 predictors based on their absolute correlation with mpg.

### Details of the Process

1.  *Data Processing*: Initially, the data is preprocessed to ensure it is ready for analysis, handling missing values and encoding categorical variables.
2.  *Correlation Calculation*: The function calculates the Pearson correlation coefficient for each predictor against the response variable, considering only complete cases.
3.  *Feature Selection*: It sorts the predictors by the absolute value of their correlation and returns the names of the top specified number (top_k) of predictors.

### Conclusion

The pre_screen_predictors_corr function is an efficient tool for preliminary feature selection in any predictive modeling process. By identifying strong linear relationships, it allows for a focused approach in subsequent model development stages.
